Index measures for oak decline severity using phenotypic descriptors

### 2019-12-15 manuscript/manuscript.Rmd
added acknowledgements

Diameter at breast height (DBH) was collected at a stem height of 1.3m, to the nearest 0.1cm.
Total height, timber hight and lowest live crown were measured using an inclinometer to the nearest 0.1m
The timber height was measured at either 7cm top stem diameter or where no main stem could be distinguished.
For the crown, canopy closure, missing crown and absolute crown density percentages were visually estimated within 5% classes

@@

- Scalability of method for wider application
- Accessability of collecting descriptors
- Discussion of applications to forestry monitoring and management
- Sensitivity for integration with molecular data compared to categorical assignments
- Sensitivity provided for integration with large scale omics analyses as well as long term monitoring for forest condition
- Refinement of protocol for large scale surveying

@@

\newpage
## Checks

>>>>

Diameter at breast height (DBH) was collected at a stem height of 1.3m, to the nearest 0.1cm.
Total height, timber height and lowest live crown were measured using an inclinometer to the nearest 0.1m
The timber height was measured at either 7cm top stem diameter or where no main stem could be distinguished.
For the crown, canopy closure, missing crown and absolute crown density percentages were visually estimated within 5% classes

@@

- Scalability of method for wider application
- Accessibility of collecting descriptors
- Discussion of applications to forestry monitoring and management
- Sensitivity for integration with molecular data compared to categorical assignments
- Sensitivity provided for integration with large scale omics analyses as well as long term monitoring for forest condition
- Refinement of protocol for large scale surveying

@@

## Acknowledgements

We would like to thank the Forest Research TSU for collecting the phenotypic data presented in this article especially Liz Richardson and Mark Oram for coordinating surveying.
This work was supported by Woodland Heritage and the Future Proofing Plant Health (FPPH) Oak Resilience project.

## Checks
